\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-10 latex/paper_sensores/paper.tex
alguna cosa mas del paper

\subsection{Accelerometer}
Due to construction issues the sensibility axis of the device are generaly not orthogonals. Let $\mathbf{a}^a$ be the acceleration measured by the accelerometer and let $\mathbf{a}^p$.

>>>>

\subsection{Accelerometer}
Due to construction issues the sensibility axis of the device are generaly not orthogonals. Lets define a platform system as shown in figure \ref{fig:mongoose}Let $\mathbf{a}^a$ be the acceleration measured by the accelerometer and let $\mathbf{a}^p$ the acceleration measured in the platform system. We model this fact by the following linear transformation between the two acceleration vectors:

\begin{equation}
\mathbf{a}^p = \mathbf{T}_a^p\mathbf{a}^a, \; \mathbf{T}_a^p = \left(\begin{array}{ccc}
1 & - \alpha_{yz} & \alpha_{zy}\\
\alpha_{xz} & 1 & - \alpha_{zx}\\
-\alpha_{xy} & \alpha_{yx} & 1
\end{array}\right)
\end{equation}
